Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-04-04 accessPEP.Rmd
fixed rho max vals in se analyses + figM1

gg_district %>%
  left_join(results_all_base, by = c("id" = "names")) -> gg_district_burden

p <- ggplot() +
  geom_polygon(data = gg_district_burden, aes(x = long, y = lat, group = group, 
                                              fill = deaths_mean/pop*1e5), 
               color = "grey50") +
  geom_point(data = ctar_points, aes(x = LONGITUDE, y = LATITUDE), color = "blue") + 
  scale_fill_gradient(low = "white", high = "red", name = "Annual deaths per 100k \n persons") +
  labs(tag = "B") +
  facet_grid(covar_name~model)

@@

### S5. Sensitity analyses for burden estimates
```{r district scaling w/ pop, cache = TRUE}
## Dist ttimes
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
dist_ttimes <- as.data.table(dist_ttimes)
dist_ttimes$mdg_dis_co <- as.character(mada_district$mdg_dis_co)
dist_ttimes <- melt(dist_ttimes, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_ttimes$scenario <- as.numeric(gsub("result.", "", dist_ttimes$scenario))
dist_ttimes <- rbind(dist_ttimes, 
                       as.data.frame(list(mdg_dis_co = dist_catchments$mdg_dis_co, scenario = 0,
                                          ttimes = dist_catchments$ttimes_weighted)))
dist_ttimes %>%
  left_join(select(mada_district@data, mdg_dis_co, district, pop = pop2015adj)) -> dist_ttimes

## Pop scaling
p_rabid_vals <- c(0.2, 0.3, 0.4, 0.5, 0.6)
rho_max_vals <- c(0.80, 0.85, 0.9, 0.95, 0.9)

>>>>

gg_district %>%
  left_join(results_all_base, by = c("id" = "names")) -> gg_district_burden
```

```{r burden figure}
p <- ggplot() +
  geom_polygon(data = gg_district_burden, aes(x = long, y = lat, group = group, 
                                              fill = deaths_mean/pop*1e5), 
               color = "grey50") +
  geom_point(data = ctar_metadata, aes(x = LONGITUDE, y = LATITUDE), color = "blue") + 
  scale_fill_gradient(low = "white", high = "red", name = "Annual deaths per 100k \n persons") +
  labs(tag = "B") +
  facet_grid(covar_name~model)

@@

### S5. Sensitity analyses for burden estimates
```{r district scaling w pop, cache = TRUE}
## Dist ttimes
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
dist_ttimes <- as.data.table(dist_ttimes)
dist_ttimes$mdg_dis_co <- as.character(mada_district$mdg_dis_co)
dist_ttimes <- melt(dist_ttimes, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_ttimes$scenario <- as.numeric(gsub("result.", "", dist_ttimes$scenario))
dist_ttimes <- rbind(dist_ttimes, 
                       as.data.frame(list(mdg_dis_co = dist_catchments$mdg_dis_co, scenario = 0,
                                          ttimes = dist_catchments$ttimes_weighted)))
dist_ttimes %>%
  left_join(select(mada_district@data, mdg_dis_co, district, pop = pop2015adj)) -> dist_ttimes

## Pop scaling
p_rabid_vals <- c(0.2, 0.3, 0.4, 0.5, 0.6)
rho_max_vals <- c(0.80, 0.85, 0.9, 0.95, 0.99)
